---
title: "Vincent_Jin_Mini_Assignment2"
author: "Vincent Jin"
date: "2023-03-31"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Mini Assignment2
## Vincent Jin

``` {r}
library(tidyverse)
```

# ============================================================ 
# 	Mini-assignment # 2
# ============================================================ 

# write your R code after each of the questions (1 to 5)
# no need to include the results of your code (i.e., only the commands are needed)

# (1) calculate the following equation: 12 plus 8 plus 20, then divide by 10 all in one line)

``` {r}
print((12 + 8 + 20) / 10)
```

# (2) calculate the following equation: 30 plus 15 plus 5, then multiply by 20, subtract by 500, and finally divide by 25 (all in one line)

``` {r}
print(((30 + 15 + 5) * 20 - 500) / 25)
```

# (3) find rounded (5 decimals), floor, and ceiling of: 1.0005678

``` {r}
x <- 1.0005678
round(x, 5)
floor(x)
ceiling(x)
```

# (4) print the patient's name of "DANIEL" in lowercase (note that the original string is in uppercase) 

``` {r}
patient <- "DANIEL"
print(tolower(patient))
```

# (5) concatenate and print three diagnosis names of "Diabetes", "Peripheral Artery Disease", "Intermittent Claudication" separated by this character " > "

``` {r}
print(paste('Diabetes', 'Peripheral Artery Disease', 'Intermittent Claudication', sep = ' > ')) 
```